The non-random assembly of functional motifs in plant-pollinator networks worldwide

### 2022-03-21 Manuscript/Main_text/Main_text_Oikos.Rmd
work in progress

@@

F
```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al. (2020). This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles). This was done by network (light blue transparent dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
library(lme4)
library(nlme)
library(tidyverse)
source("../../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
d <- add_study_id(d)
#str(d)
#head(d)

@@

*Acknowledgements* - This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2). We would like to thank David García-Callejas for useful comments on the manuscript before submission. Finally, JBL also thanks the University of New England for the funding provided to carry out this work.

>>>>

**Overview**

To investigate the structure of the meso-scale in plant-pollinator networks, we have gathered 60 published plant-pollinator networks with worldwide distribution. Then, we have divided the plant and floral visitor species from these networks into groups that summarize their main life-history strategies. After, we calculated the normalize motif frequencies and investigated if these frequencies are similar to the ones expected by chance with thelp of null models. Then, we have also calculated the normalize group frequencies for the different motif positions and investigated also over- and under-representation of the group frequencies.

: (i) gathered 60 published plant-pollinator networks with worldwide distribution; (ii) determined the main plant and floral visitor groups that summarize the principal life-history strategies of the species in these networks; (iii) calculated the normalized motif frequencies and compare them with the expected frequencies from null models from the same set of plant-pollinator networks; (iv) calculated the normalise frequencies of the different plant and floral visitor groups and compare them with the ones from null models; (v) explore the association

the structure of the meso-scale of plant-pollinator networks we have gathered 60 networks with worldwide distribution. Then, we have determined for the different plant and floral visitor the main groups that define the principal life-history strategies. After, we have calculated the normalize motif frequencies in this same set of plant-pollinator networks and investigated if the overall motif frequencies concur or not with the expected frequencies from null models originated from the same set of networks. Then,

After, we have calculated the frequencies of the different plant and floral visitor groups and explore if these frequencies also match the expected from null models or not. Finally, we investigate if the plant and floral visitor motif combinations can be retrieve from their expected probability or not by assuming

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al. (2020). This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles). This was done by network (light blue transparent dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}

library(lme4)
library(nlme)
library(tidyverse)
source("../../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
d <- add_study_id(d)
#str(d)
#head(d)

@@

*Acknowledgements* - This study was supported by the European project SAFEGUARD (101003476 H2020-SFS-2019-2). JBL also thanks the University of New England for the funding provided to carry out this work. Finally, we would like to thank David García-Callejas for his useful comments on the manuscript before submission.
